---
title: "read_results_cluster"
editor_options: 
  chunk_output_type: console
---

```{r libs}
# library(MASS)
# library(matrixcalc)
library(Matrix)
library(tidyr)
library(ggplot2)

library(fabletools)
library(fable)
library(feasts)
library(tsibble)
library(dplyr)

# library(devtools)
# load_all()
library(ReconCov)
library(purrr)
```


# Read

```{r}
S <- readRDS("tourism/data/S.rds")
row_names <- readRDS("tourism/data/row_names.rds")
seq_dates <- readRDS("tourism/job/seq_dates.rds")
visnights_full <- readRDS("tourism/data/visnights_full.rds")

path <- "D:/Github/tourism_cluster/results/" # new results

M <- 133

result_list_full <- list()
for (i in 1:M) {
  if (i == 19) next # iteration 19 has error
  result <- readRDS(paste0(path, "result_", i, ".rds")) 
  # result_list[[i]] <- result
  result_list_full[[i]] <- result[-3] # not taking the base fitted models
}
result_list <- result_list_full[-19]

# remove the last 3 years of results
M <- M - 3*12 - 1 # -1 for the removed iteration 19
result_list <- result_list[1:M]

# flatten out the sublist in `e`
flatten_e_list <- function(e_list) {
  out <- list()

  for (name in names(e_list)) {
    obj <- e_list[[name]]

    if (is.list(obj) && all(vapply(obj, is.matrix, logical(1)))) {
      ## e.g. name == "mint_shr_pc", obj contains K1 … K20
      for (k in names(obj)) {
        out[[paste(name, k, sep = "_")]] <- obj[[k]]   # “mint_shr_pc_K1”, …
      }
    } else {
      out[[name]] <- obj                               # “base”, “ols”, …
    }
  }
  out                                             # all matrices at top level
}
all_model_names <- names(flatten_e_list(result_list[[1]]$e))


h <- 12
# model_names <- c("base", "ols", "mint_shr", "mint_n")
SSE_cum <- setNames(
  lapply(all_model_names, function(name) {
    matrix(0, h, length(rownames(S)), dimnames = list(1:h, rownames(S)))
  }),
  all_model_names
)
# wrangle
# SSE_cum <- Reduce(function(acc, res) Map(`+`, acc, res$e2),
#                       result_list, init = SSE_cum)

# need to square the errors first
SSE_cum <- Reduce(
  function(acc, res) {
    e_flat <- flatten_e_list(res$e)
    Map(function(x, y) x + y^2, acc, e_flat[ names(acc) ])   # element-wise matrix addition
  },
  result_list,
  init = SSE_cum
)

  
# W_shr_store <- sapply(result_list, `[[`, "W_shr")
# W_n_store <- t(sapply(result_list, `[[`, "W_n")) ; colnames(W_n_store) <- c("lambda", "delta")

MSE <- lapply(SSE_cum, function(mat) mat / M)
```



# Evaluation

## Average plots

```{r}
MSE_ts <- transform_sim_MSE(MSE, F)

# MSE plot
MSE_ts |> group_by(.model, h) |>
  summarise(mse = mean(MSE)) |>
  filter(.model != "mint_sample") |> 
  ggplot(aes(x = h, y = mse, color = .model)) +
    geom_line() +
    labs(x = "Horizon", y = "MSE") +
    theme_minimal()

# % improv plot
MSE_ts |>
  # filter models
  # filter(.model %in% c("base", "ols", "mint_shr", "mint_n")) |>
  # filter(!grepl("K10|K20", .model)) |>
  # filter(grepl("mint_n", .model)) |>
  group_by(series, h) |>
  mutate(
    base_MSE = MSE[.model == "base"]
  ) |>
  ungroup() |>
  group_by(.model, h) |>
  summarise(
    MSE = mean(MSE),
    base_MSE = mean(base_MSE),
    pct_change = (MSE - base_MSE) / base_MSE * 100
  ) |>
  ggplot(aes(x = h, y = pct_change, color = .model)) +
  geom_line() +
  labs(x = "Horizon", y = "% improvements",
       title = "% relative improvements in MSE compared to Base",
       subtitle = "training size = 120, iterations = 96") +
  theme_minimal()
```

```{r}
improv_overtime <- matrix(0, 96, length(all_model_names),
  dimnames = list(1:96, all_model_names)
)

for (i in 1:96) {
  res <- result_list[[i]]
  for (model in model_names) {
    if (model == "base")
      improv_overtime[i, model] <- mean(res$e2[[model]][1,])
    else
      improv_overtime[i, model] <- (mean(res$e2[[model]][1,]) - improv_overtime[i, "base"]) / improv_overtime[i, "base"] * 100
  }
}

improv_overtime[, 2:4] |>            # keep the three models
  as.data.frame() |>
  cbind(Month = seq_dates$end) |> 
  pivot_longer(-Month,
               names_to  = "model",
               values_to = "pct_improve") |> 
  ggplot(aes(x = Month, y = pct_improve, color = model)) +
    geom_line() +
    labs(x = "Month", y = "% improvements",
         title = "% relative improvements in average error squared compared to Base for each iteration") +
    theme_minimal()

```


## At each level

```{r get levels}
series <- rownames(S)

level_index <- set_names(
  vector("list", 8),
  c(
    "Australia", "State", "Zone", "Region",
    "Australia_by_Purpose", "State_by_Purpose", 
    "Zone_by_Purpose", "Region_by_Purpose"
  )  
)
level_index$Australia <- which(series == "Total")
level_index$State <- which(series %in% names(state_map))
level_index$Zone <- which(series %in% names(zone_map))
level_index$Region <- which(series %in% unlist(state_map, use.names = F))

# find indices for series by purpose
series_split <- strsplit(series, " - ")
purposes <- c("Business", "Holiday", "Visiting friends and relatives", "Other reason")
level_index$Australia_by_Purpose <- which(series %in% purposes)
level_index$State_by_Purpose <- which(
  sapply(series_split, function(x) length(x) == 2 && 
         x[1] %in% names(state_map))
)
level_index$Zone_by_Purpose <- which(
  sapply(series_split, function(x) length(x) == 2 && 
         x[1] %in% names(zone_map))
)
level_index$Region_by_Purpose <- which(
  sapply(series_split, function(x) length(x) == 2 && 
         x[1] %in% unlist(state_map, use.names = F))
)


# similar to for key, value in dict.items() in Python
level_map <- imap(level_index, function(value, key){
  set_names(rep(key, length(value)), series[value])
}) |> 
  flatten_chr()

desired_order <- c(
  "Australia", "Australia_by_Purpose",
  "State",     "State_by_Purpose",
  "Zone",      "Zone_by_Purpose",
  "Region",    "Region_by_Purpose"
)
```

```{r}
# MSE at each level
MSE_ts <- MSE_ts %>% 
  mutate(
    level = level_map[series] %||% NA_character_,
    # %||% is just “if lookup returns NULL, fall back to NA
    level = factor(
      level,
      levels = desired_order,
      labels = str_replace_all(desired_order, "_", " ")  # replace "_" with " "
    )
  )

# % improv plot by level
MSE_ts |>
  # # # filter models
  # filter(!grepl("K10|K20", .model)) |>
  # filter(!grepl("mint_shr", .model)) |> 
  # filter(.model == "base" | grepl("K1", .model)) |>
  filter(.model %in% c("base", "ols", "mint_n", "mint_shr")) |>
  group_by(series, h) |>
  mutate(
    base_MSE = MSE[.model == "base"]
  ) |>
  ungroup() |>
  group_by(.model, level, h) |>
  summarise(
    MSE = mean(MSE),
    base_MSE = mean(base_MSE),
    pct_change = (MSE - base_MSE) / base_MSE * 100
  ) |>
  filter(.model != "mint_sample") |> 
  ggplot(aes(x = h, y = pct_change, color = .model)) +
    geom_line() +
    labs(x = "Horizon", y = "% improvements",
         title = "% relative improvements in MSE compared to Base") +
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    theme_minimal()
```

# Probabilistic Evaluation

## Get winkler & CRPS score

```{r}
library(distributional)

M <- length(result_list_full)
model_names <- all_model_names[!grepl("K5|K10|K20", all_model_names)] # remove pc models
model_names <- c(model_names, "ols_shr") # add ols_shr

#   row - CV iterations
#   col - series
result_winklers_80 <- setNames(
  lapply(model_names, function(name) {
    matrix(0, M, length(rownames(S)), dimnames = list(1:M, rownames(S)))
  }),
  model_names
)
result_winklers_95 <- result_winklers_80
result_crps <- result_winklers_80

# Get actual data
y <- visnights_full |> 
  as_tibble() |> 
  arrange(State, Region) |>
  left_join(row_names, by = c("State", "Zone", "Region", "Purpose")) |>
  select(name, Nights, Month) |>
  pivot_wider(names_from = name, values_from = Nights) |>
  select(-Month) |>
  as.matrix()
y <- y[, rownames(S)]

vectorise_winkler <- function(mu, sd, actual, interval) {
  if (length(mu) == 0 || length(sd) == 0) {
    stop("mu or sd empty")
  }
  sapply(
    rownames(S),
    function(series) winkler_score(
      dist_normal(mu[series], sd[series]),
      actual[series],
      interval
    )
  )
}

vectorise_crps <- function(mu, sd, actual) {
  if (length(mu) == 0 || length(sd) == 0) {
    stop("mu or sd empty")
  }
  sapply(
    rownames(S),
    function(series) CRPS(
      dist_normal(mu[series], sd[series]),
      actual[series]
    )
  )
}

start_date <- seq_dates$start[1]

for (i in 1:M) {
  
  if (i == 19) next # iteration 19 has error
  result <- result_list_full[[i]]
  result$e <- flatten_e_list(result$e) # flatten the list of errors
  resid <- result$resid

  actual <- y[seq_dates$end[i] + 1 - start_date + 1, ] # 1-step ahead actuals

  # Recover a list of W1_hat for each model
  W1_hats <- list()
  W1_hats[["base"]] <- cov(resid) # sample variance of 1-step-ahead residuals as a proxy
  W1_hats[["ols"]] <- W1_hats[["base"]]

  W1_hats[["mint_shr"]] <- shrinkage_est(resid, result$W_shr[1])$cov
  W1_hats[["mint_n"]] <- novelist_est(resid, result$W_n["delta", 1], result$W_n["lambda", 1])$cov
  rownames(W1_hats[["mint_n"]]) <- colnames(W1_hats[["mint_n"]]) <- rownames(S)
  # pc models
  W1_hats[["mint_shr_pc_K1"]] <- shrinkage_pc_est(resid, 1, result$W_shr[2])$cov
  W1_hats[["mint_shr_pc_K2"]] <- shrinkage_pc_est(resid, 2, result$W_shr[3])$cov
  W1_hats[["mint_n_pc_K1"]] <- novelist_pc_est(resid, 1, result$W_n["delta", 2], result$W_n["lambda", 2])$cov
  W1_hats[["mint_n_pc_K2"]] <- novelist_pc_est(resid, 2, result$W_n["delta", 3], result$W_n["lambda", 3])$cov

  W1_hats[["ols_shr"]] <- shrinkage_est(resid)$cov
  
  for (model in model_names) {

    if (model == "base") {
      base_fc <- actual - result$e$base[1, ] # recover 1-step ahead base forecast

      # Winkler score for base model
      result_winklers_80[[model]][i, ] <- vectorise_winkler(
        base_fc, sqrt(diag(W1_hats[[model]])), actual, 80
      )
      result_winklers_95[[model]][i, ] <- vectorise_winkler(
        base_fc, sqrt(diag(W1_hats[[model]])), actual, 95
      )
      # CRPS for base model
      result_crps[[model]][i, ] <- vectorise_crps(
        base_fc, sqrt(diag(W1_hats[[model]])), actual
      )

    } else {
      # obtain mapping G
      if (model %in% c("ols", "ols_shr")) {
        G <- solve(t(S) %*% S) %*% t(S)
      } else {
        P <- t(S) %*% solve(W1_hats[[model]])
        G <- solve(P %*% S) %*% P
      }
      # get reconciled forecast and covariance
      if (model == "ols_shr") {
        # ols_shr uses ols reconciled forecast
        y_recon <- actual - result$e[["ols"]][1, ]
      } else {
        y_recon <- actual - result$e[[model]][1, ]
      }
      W1_recon <- S %*% G %*% W1_hats[[model]] %*% t(G) %*% t(S)

      # Winkler score for reconciled model
      result_winklers_80[[model]][i, ] <- vectorise_winkler(
        mu = y_recon, sd = sqrt(diag(W1_recon)), actual, 80
      )
      result_winklers_95[[model]][i, ] <- vectorise_winkler(
        mu = y_recon, sd = sqrt(diag(W1_recon)), actual, 95
      )
      # CRPS for reconciled model
      result_crps[[model]][i, ] <- vectorise_crps(
        mu = y_recon, sd = sqrt(diag(W1_recon)), actual
      )
    }
  }
  cat("Done", i, "\n")
}

# remove 19th row
nrow(result_winklers_95[[1]])
result_winklers_80 <- lapply(result_winklers_80, function(mat) mat[-19, ])
result_winklers_95 <- lapply(result_winklers_95, function(mat) mat[-19, ])
result_crps <- lapply(result_crps, function(mat) mat[-19, ])

# saveRDS(result_winklers_80, "tourism/job/results/result_winklers_80.rds")
# saveRDS(result_winklers_95, "tourism/job/results/result_winklers_95.rds")
# saveRDS(result_crps, "tourism/job/results/result_crps.rds")
```

## Wrangle and plots
```{r}
library(stringr)

result_winklers_80 <- readRDS("tourism/job/results/result_winklers_80.rds")
result_winklers_95 <- readRDS("tourism/job/results/result_winklers_95.rds")
result_crps <- readRDS("tourism/job/results/result_crps.rds")

score_df <- result_crps |> 
  transform_sim_MSE(F) |> 
  # change column name "h" to "iter", "MSE" to "score"
  rename(iter = h, score = MSE)

# wrangle
{
  # add level
  score_df <- score_df %>% 
    mutate(
      level = level_map[series] %||% NA_character_,
      # %||% is just “if lookup returns NULL, fall back to NA
      level = factor(
        level,
        levels = desired_order,
        labels = str_replace_all(desired_order, "_", " ")  # replace "_" with " "
      )
    )
  # filter pc2 models
  score_df <- score_df %>%
    filter(!grepl("K2", .model)) # remove pc2 models

  # filter last 3 years
  score_df <- score_df %>%
    filter(iter <= M - 12*3 - 1) # keep only the first M iterations

  # average of % improvements per series
  score_df <- score_df |>
    group_by(series, iter) |>
    mutate(
      base_score = score[.model == "base"]
    ) |>
    ungroup() |>
    mutate(pct_change_per_series = (score - base_score) / base_score * 100)
}
```

```{r pct over average}
# # winklers per model
# score_df |> 
#   group_by(.model) |>
#   summarise(score = mean(score)) |>
#   ggplot(aes(x = .model, y = score)) +
#     geom_col() +
#     labs(x = "Model", y = "Winkler score",
#          title = "Average Winkler scores for each model") +
#     theme_minimal()

# # winklers improvements per model
# score_df |>
#   group_by(series, iter) |>
#   mutate(
#     base_score = score[.model == "base"]
#   ) |>
#   ungroup() |>
#   group_by(.model) |>
#   summarise(
#     score = mean(score),
#     base_score = mean(base_score),
#     pct_change = (score - base_score) / base_score * 100
#   ) |> 
#   ggplot(aes(x = .model, y = pct_change, fill = .model)) +
#     geom_col() +
#     labs(x = "Model", y = "% improvements",
#          title = "% relative improvements in CRPS compared to Base",
#          subtitle = "Interpret: negative values indicate improvement.") +
#     theme_minimal()

# # winklers improvements per model per level
# score_df |>
#   group_by(series, iter) |>
#   mutate(
#     base_score = score[.model == "base"]
#   ) |>
#   ungroup() |>
#   group_by(.model, level) |>
#   summarise(
#     score = mean(score),
#     base_score = mean(base_score),
#     pct_change = (score - base_score) / base_score * 100
#   ) |> 
#   ggplot(aes(x = .model, y = pct_change, fill = .model)) +
#     geom_col(position = "dodge") +
#     labs(x = "Level", y = "% improvements",
#          title = "% relative improvements in CRPS compared to Base",
#          subtitle = "Interpret: negative values mean improvement") +
#     facet_wrap(~ level, ncol=2, scales = "free_y") +
#     theme_minimal()
```

## Average of % improvements
```{r}
score_label <- "W95"
score_df |> 
  group_by(.model) |> 
  summarise(
    pct_change_avg = mean(pct_change_per_series)
  ) |> 
  ggplot(aes(x = .model, y = pct_change_avg, fill = .model)) +
    geom_col() +
    labs(x = "Model", y = "% improvements",
         title = paste("Average of % relative improvements in", score_label, "compared to Base"),
         subtitle = "Interpret: negative values indicate improvement. Avg over pct") +
    theme_minimal()

score_df |> 
  group_by(.model, level) |> 
  summarise(
    pct_change_avg = mean(pct_change_per_series)
  ) |> 
  ggplot(aes(x = .model, y = pct_change_avg, fill = .model)) +
    geom_col(position = "dodge") +
    labs(x = "Level", y = "% improvements",
         title = paste("Average of % relative improvements in", score_label, "compared to Base"),
         subtitle = "Interpret: negative values mean improvement. Avg over pct") +
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    theme_minimal()  
```



## lolipop plots
```{r}
library(tidytext)
pef_model <- "mint_shr"

plot_df <- score_df |> 
  group_by(series, level, .model) |> 
  summarise(pct_change_avg = mean(pct_change_per_series), .groups = "drop") |>
  # set every pct >= x to x
  mutate(pct_change_avg = pmin(pct_change_avg, 10)) |> 
  # sort series by pct_change_avg of mint_n_pc_K1
  # mutate(series = fct_reorder(series, pct_change_avg[.model == "mint_n_pc_K1"])) |>  
  # filter(level == "Region") |>
  filter(!grepl("K2", .model)) |> 
  mutate(level_group = case_when(
    level %in% c("Australia", "Australia by Purpose", "State", "State by Purpose") ~ "1.High levels",
    level %in% c("Zone", "Zone by Purpose") ~ "2.Zone & Zone by Purpose",
    level == "Region" ~ "3.Region",
    level == "Region by Purpose" ~ "4.Region by Purpose",
    TRUE ~ NA_character_
  )) |>
  group_by(level_group, series) |>
  mutate(order_key = pct_change_avg[.model == pef_model][1]) |>
  ungroup() |>
  mutate(order_key = if_else(is.na(order_key), -Inf, order_key),
         series_ord = reorder_within(series, order_key, level_group, .desc = TRUE))


ggplot(plot_df, aes(x = series_ord, y = pct_change_avg)) +
  geom_segment(aes(xend = series_ord, yend = 0), color = "grey") +
  geom_point(aes(color = .model, shape = .model), size = 2) +
  coord_flip() +
  facet_wrap(~ level_group, nrow = 2, scales = "free_y") + # free_y drops unused levels per facet
  scale_x_reordered() +                                    # remove the internal suffix used by reorder_within
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        legend.position = "bottom") +
  labs(x = "Series", y = "% improvements",
       title = "Average of % relative improvements in CRPS compared to Base",
       subtitle = "Negative values mean improvement; values ≥ 30% are capped at 30%")
```


## Get Energy Score

Need sampling to approximate the energy score.
To ensure coherency, we sample from the reconciled distribution of the bottom-level series, then aggregate up to obtain all levels.

mu_b = G * mu
W_b = G * W * G^T
b_sample ~ N(mu_b, W_b)
y_sample = S * b_sample

Calculate energy score from y_samples and actuals

```{r}
coherent_draws <- function(mu_base, Sigma_base, S, G, m) {
  # mu: vector of base forecast means (all series)
  # Sigma: covariance matrix of base forecast (all series)
  
  mu_bot <- G %*% mu_base
  Sigma_bot <- G %*% Sigma_base %*% t(G)
  
  b_samples <- MASS::mvrnorm(m, mu_bot, Sigma_bot) # m x p_bottpm
  y_samples <- t(S %*% t(b_samples))           # m x p
  return(y_samples)
}

energy_score_from_samples <- function(samples, actual) {
  m <- nrow(samples)
  term1 <- mean(sqrt(rowSums(
    (sweep(samples, 2, actual, "-"))^2
  )))
  term2 <- mean(sqrt(rowSums(
    (samples[sample(1:m, m, replace = TRUE), ] - samples[sample(1:m, m, replace = TRUE), ])^2
  )))
  return(term1 - 0.5 * term2)
}
```



```{r}
library(distributional)

M <- length(result_list_full)
model_names <- all_model_names[!grepl("K5|K10|K20", all_model_names)] # remove pc models
model_names <- c(model_names, "base_shr", "ols_shr") # add base_shr ols_shr FOR MULTIVARIATE ONLY

#   row - CV iterations
#   col - models
result_energy <- matrix(0, M, length(model_names),
  dimnames = list(1:M, model_names)
)

# Get actual data
y <- visnights_full |> 
  as_tibble() |> 
  arrange(State, Region) |>
  left_join(row_names, by = c("State", "Zone", "Region", "Purpose")) |>
  select(name, Nights, Month) |>
  pivot_wider(names_from = name, values_from = Nights) |>
  select(-Month) |>
  as.matrix()
y <- y[, rownames(S)]

start_date <- seq_dates$start[1]
m <- 10000 # number of samples

for (i in 1:M) {
  
  if (i == 19) next # iteration 19 has error
  result <- result_list_full[[i]]
  result$e <- flatten_e_list(result$e) # flatten the list of errors
  resid <- result$resid

  actual <- y[seq_dates$end[i] + 1 - start_date + 1, ] # 1-step ahead actuals

  # Recover a list of W1_hat for each model
  W1_hats <- list()
  W1_hats[["base"]] <- nearPD(cov(resid))$mat |> as.matrix() # sample variance of 1-step-ahead residuals as a proxy
  W1_hats[["ols"]] <- W1_hats[["base"]]

  W1_hats[["mint_shr"]] <- shrinkage_est(resid, result$W_shr[1])$cov
  W1_hats[["mint_n"]] <- novelist_est(resid, result$W_n["delta", 1], result$W_n["lambda", 1])$cov
  rownames(W1_hats[["mint_n"]]) <- colnames(W1_hats[["mint_n"]]) <- rownames(S)
  # pc models
  W1_hats[["mint_shr_pc_K1"]] <- shrinkage_pc_est(resid, 1, result$W_shr[2])$cov
  W1_hats[["mint_shr_pc_K2"]] <- shrinkage_pc_est(resid, 2, result$W_shr[3])$cov
  W1_hats[["mint_n_pc_K1"]] <- novelist_pc_est(resid, 1, result$W_n["delta", 2], result$W_n["lambda", 2])$cov
  W1_hats[["mint_n_pc_K2"]] <- novelist_pc_est(resid, 2, result$W_n["delta", 3], result$W_n["lambda", 3])$cov

  W1_hats[["base_shr"]] <- shrinkage_est(resid)$cov   # FOR MULTIVARIATE ONLY
  W1_hats[["ols_shr"]] <- W1_hats[["base_shr"]]
    
  for (model in model_names) {

    if (model %in% c("base", "base_shr")) {
      base_fc <- actual - result$e$base[1, ] # recover 1-step ahead base forecast

      # Energy score for base model
      samples <- MASS::mvrnorm(m, base_fc, W1_hats[[model]])
      result_energy[i, model] <- energy_score_from_samples(samples, actual)

    } else {
      # obtain mapping G
      if (model %in% c("ols", "ols_shr")) {
        G <- solve(t(S) %*% S) %*% t(S)
      } else {
        P <- t(S) %*% solve(W1_hats[[model]])
        G <- solve(P %*% S) %*% P
      }
      # Energy score for reconciled model
      samples <- coherent_draws(base_fc, W1_hats[[model]], S, G, m)
      result_energy[i, model] <- energy_score_from_samples(samples, actual)
    }
  }
  cat("Done", i, "\n")
}
```



```{r}
saveRDS(result_energy, "tourism/job/results/result_energy_10k.rds")

readRDS("tourism/job/results/result_energy_10k.rds") -> result_energy

# remove 19th row
if (all(result_energy[19, ] == 0)) {
  cat("Removing 19th row\n")
  result_energy <- result_energy[-19, ]
}

{
  energy_df <- result_energy |> 
    as_tibble(rownames = "iter") |>
    pivot_longer(-iter, names_to = ".model", values_to = "score") |>
    mutate(iter = as.integer(iter))
  # filter last 3 years
  energy_df <- energy_df |> 
    filter(iter <= M - 12*3 - 1) # keep only the first M iterations
  # pct change
  energy_df <- energy_df |> 
    group_by(iter) |>
    mutate(
      base_score = score[.model == "base"],
      pct_change_per_series = (score - base_score) / base_score * 100
    )
}
```

## Plots

```{r}
# overall energy score per model
energy_df |> 
  group_by(.model) |> 
  summarise(
    mean_score = mean(score),
    pct_change_avg = mean(pct_change_per_series)
  ) |>
  ggplot(aes(x = .model, y = pct_change_avg, fill = .model)) +
    geom_col() +
    labs(x = "Model", y = "% improvements",
         title = "Average of % relative improvements in Energy Score compared to Base",
         subtitle = "Negative values indicate improvement. Avg over pct. Test set ends 2016") +
    theme_minimal()
```