---
title: "read_results_cluster"
editor_options: 
  chunk_output_type: console
---

```{r libs}
# library(MASS)
# library(matrixcalc)
library(Matrix)
library(tidyr)
library(ggplot2)

library(fabletools)
library(fable)
library(feasts)
library(tsibble)
library(dplyr)
library(tibble)
library(fmsb) #radarchart
library(distributional)

# library(devtools)
# load_all()
library(ReconCov)
library(purrr)

source("R/helpers.R")
```


# Read

```{r}
S <- readRDS("tourism/data/S.rds")
row_names <- readRDS("tourism/data/row_names.rds")
seq_dates <- readRDS("tourism/job/seq_dates.rds")
visnights_full <- readRDS("tourism/data/visnights_full.rds")

path <- "D:/Github/tourism_cluster/results/" # new results

M <- 133

result_list_full <- list()
for (i in 1:M) {
  # if (i == 19) next # iteration 19 has error
  result <- readRDS(paste0(path, "result_", i, ".rds")) 
  # result_list[[i]] <- result
  result_list_full[[i]] <- result[-3] # not taking the base fitted models
}
# result_list <- result_list_full[-19]

# remove the last 3 years of results
M <- M - 3*12 
result_list <- result_list[1:M]

# flatten out the sublist in `e`
flatten_e_list <- function(e_list) {
  out <- list()

  for (name in names(e_list)) {
    obj <- e_list[[name]]

    if (is.list(obj) && all(vapply(obj, is.matrix, logical(1)))) {
      ## e.g. name == "mint_shr_pc", obj contains K1 … K20
      for (k in names(obj)) {
        out[[paste(name, k, sep = "_")]] <- obj[[k]]   # “mint_shr_pc_K1”, …
      }
    } else {
      out[[name]] <- obj                               # “base”, “ols”, …
    }
  }
  out                                             # all matrices at top level
}
all_model_names <- names(flatten_e_list(result_list[[1]]$e))


h <- 12
# model_names <- c("base", "ols", "mint_shr", "mint_n")
SSE_cum <- setNames(
  lapply(all_model_names, function(name) {
    matrix(0, h, length(rownames(S)), dimnames = list(1:h, rownames(S)))
  }),
  all_model_names
)
# wrangle
# SSE_cum <- Reduce(function(acc, res) Map(`+`, acc, res$e2),
#                       result_list, init = SSE_cum)

# need to square the errors first
SSE_cum <- Reduce(
  function(acc, res) {
    e_flat <- flatten_e_list(res$e)
    Map(function(x, y) x + y^2, acc, e_flat[ names(acc) ])   # element-wise matrix addition
  },
  result_list,
  init = SSE_cum
)

  
# W_shr_store <- sapply(result_list, `[[`, "W_shr")
# W_n_store <- t(sapply(result_list, `[[`, "W_n")) ; colnames(W_n_store) <- c("lambda", "delta")

MSE <- lapply(SSE_cum, function(mat) mat / M)
```



# Evaluation

## Average plots

```{r}
MSE_ts <- transform_sim_MSE(MSE, F)

# MSE plot
MSE_ts |> group_by(.model, h) |>
  summarise(mse = mean(MSE)) |>
  filter(.model != "mint_sample") |> 
  ggplot(aes(x = h, y = mse, color = .model)) +
    geom_line() +
    labs(x = "Horizon", y = "MSE") +
    theme_minimal()

# % improv plot
MSE_ts |>
  # filter models
  # filter(.model %in% c("base", "ols", "mint_shr", "mint_n")) |>
  # filter(!grepl("K10|K20", .model)) |>
  # filter(grepl("mint_n", .model)) |>
  group_by(series, h) |>
  mutate(
    base_MSE = MSE[.model == "base"]
  ) |>
  ungroup() |>
  group_by(.model, h) |>
  summarise(
    MSE = mean(MSE),
    base_MSE = mean(base_MSE),
    pct_change = (MSE - base_MSE) / base_MSE * 100
  ) |>
  ggplot(aes(x = h, y = pct_change, color = .model)) +
  geom_line() +
  labs(x = "Horizon", y = "% improvements",
       title = "% relative improvements in MSE compared to Base",
       subtitle = "training size = 120, iterations = 96") +
  theme_minimal()
```

```{r}
improv_overtime <- matrix(0, 96, length(all_model_names),
  dimnames = list(1:96, all_model_names)
)

for (i in 1:96) {
  res <- result_list[[i]]
  for (model in model_names) {
    if (model == "base")
      improv_overtime[i, model] <- mean(res$e2[[model]][1,])
    else
      improv_overtime[i, model] <- (mean(res$e2[[model]][1,]) - improv_overtime[i, "base"]) / improv_overtime[i, "base"] * 100
  }
}

improv_overtime[, 2:4] |>            # keep the three models
  as.data.frame() |>
  cbind(Month = seq_dates$end) |> 
  pivot_longer(-Month,
               names_to  = "model",
               values_to = "pct_improve") |> 
  ggplot(aes(x = Month, y = pct_improve, color = model)) +
    geom_line() +
    labs(x = "Month", y = "% improvements",
         title = "% relative improvements in average error squared compared to Base for each iteration") +
    theme_minimal()

```


## At each level

```{r get levels}
series <- rownames(S)

level_index <- set_names(
  vector("list", 8),
  c(
    "Australia", "State", "Zone", "Region",
    "Australia_by_Purpose", "State_by_Purpose", 
    "Zone_by_Purpose", "Region_by_Purpose"
  )  
)
level_index$Australia <- which(series == "Total")
level_index$State <- which(series %in% names(state_map))
level_index$Zone <- which(series %in% names(zone_map))
level_index$Region <- which(series %in% unlist(state_map, use.names = F))

# find indices for series by purpose
series_split <- strsplit(series, " - ")
purposes <- c("Business", "Holiday", "Visiting friends and relatives", "Other reason")
level_index$Australia_by_Purpose <- which(series %in% purposes)
level_index$State_by_Purpose <- which(
  sapply(series_split, function(x) length(x) == 2 && 
         x[1] %in% names(state_map))
)
level_index$Zone_by_Purpose <- which(
  sapply(series_split, function(x) length(x) == 2 && 
         x[1] %in% names(zone_map))
)
level_index$Region_by_Purpose <- which(
  sapply(series_split, function(x) length(x) == 2 && 
         x[1] %in% unlist(state_map, use.names = F))
)


# similar to for key, value in dict.items() in Python
level_map <- imap(level_index, function(value, key){
  set_names(rep(key, length(value)), series[value])
}) |> 
  flatten_chr()

desired_order <- c(
  "Australia", "Australia_by_Purpose",
  "State",     "State_by_Purpose",
  "Zone",      "Zone_by_Purpose",
  "Region",    "Region_by_Purpose"
)
```

```{r}
# MSE at each level
MSE_ts <- MSE_ts %>% 
  mutate(
    level = level_map[series] %||% NA_character_,
    # %||% is just “if lookup returns NULL, fall back to NA
    level = factor(
      level,
      levels = desired_order,
      labels = str_replace_all(desired_order, "_", " ")  # replace "_" with " "
    )
  )

# % improv plot by level
MSE_ts |>
  # # # filter models
  # filter(!grepl("K10|K20", .model)) |>
  # filter(!grepl("mint_shr", .model)) |> 
  # filter(.model == "base" | grepl("K1", .model)) |>
  filter(.model %in% c("base", "ols", "mint_n", "mint_shr")) |>
  group_by(series, h) |>
  mutate(
    base_MSE = MSE[.model == "base"]
  ) |>
  ungroup() |>
  group_by(.model, level, h) |>
  summarise(
    MSE = mean(MSE),
    base_MSE = mean(base_MSE),
    pct_change = (MSE - base_MSE) / base_MSE * 100
  ) |>
  filter(.model != "mint_sample") |> 
  ggplot(aes(x = h, y = pct_change, color = .model)) +
    geom_line() +
    labs(x = "Horizon", y = "% improvements",
         title = "% relative improvements in MSE compared to Base") +
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    theme_minimal()
```

# Probabilistic Evaluation

## Get winkler & CRPS score

```{r}
library(distributional)

M <- length(result_list_full)
model_names <- all_model_names[!grepl("K5|K10|K20", all_model_names)] # remove pc models
model_names <- c(model_names, "ols_shr") # add ols_shr

#   row - CV iterations
#   col - series
result_winklers_80 <- setNames(
  lapply(model_names, function(name) {
    matrix(0, M, length(rownames(S)), dimnames = list(1:M, rownames(S)))
  }),
  model_names
)
result_winklers_95 <- result_winklers_80
result_crps <- result_winklers_80

# Get actual data
y <- visnights_full |> 
  as_tibble() |> 
  arrange(State, Region) |>
  left_join(row_names, by = c("State", "Zone", "Region", "Purpose")) |>
  select(name, Nights, Month) |>
  pivot_wider(names_from = name, values_from = Nights) |>
  select(-Month) |>
  as.matrix()
y <- y[, rownames(S)]

vectorise_winkler <- function(mu, sd, actual, interval) {
  if (length(mu) == 0 || length(sd) == 0) {
    stop("mu or sd empty")
  }
  sapply(
    rownames(S),
    function(series) winkler_score(
      dist_normal(mu[series], sd[series]),
      actual[series],
      interval
    )
  )
}

vectorise_crps <- function(mu, sd, actual) {
  if (length(mu) == 0 || length(sd) == 0) {
    stop("mu or sd empty")
  }
  sapply(
    rownames(S),
    function(series) CRPS(
      dist_normal(mu[series], sd[series]),
      actual[series]
    )
  )
}

start_date <- seq_dates$start[1]

for (i in 1:M) {
  
  if (i == 19) next # iteration 19 has error
  result <- result_list_full[[i]]
  result$e <- flatten_e_list(result$e) # flatten the list of errors
  resid <- result$resid

  actual <- y[seq_dates$end[i] + 1 - start_date + 1, ] # 1-step ahead actuals

  # Recover a list of W1_hat for each model
  W1_hats <- list()
  W1_hats[["base"]] <- compute_cov_matrix(resid, T) # sample variance of 1-step-ahead residuals as a proxy
  W1_hats[["ols"]] <- W1_hats[["base"]]

  W1_hats[["mint_shr"]] <- shrinkage_est(resid, result$W_shr[1])$cov
  W1_hats[["mint_n"]] <- novelist_est(resid, result$W_n["delta", 1], result$W_n["lambda", 1])$cov
  rownames(W1_hats[["mint_n"]]) <- colnames(W1_hats[["mint_n"]]) <- rownames(S)
  # pc models
  W1_hats[["mint_shr_pc_K1"]] <- shrinkage_pc_est(resid, 1, result$W_shr[2])$cov
  W1_hats[["mint_shr_pc_K2"]] <- shrinkage_pc_est(resid, 2, result$W_shr[3])$cov
  W1_hats[["mint_n_pc_K1"]] <- novelist_pc_est(resid, 1, result$W_n["delta", 2], result$W_n["lambda", 2])$cov
  W1_hats[["mint_n_pc_K2"]] <- novelist_pc_est(resid, 2, result$W_n["delta", 3], result$W_n["lambda", 3])$cov

  W1_hats[["ols_shr"]] <- shrinkage_est(resid)$cov
  
  for (model in model_names) {

    if (model == "base") {
      base_fc <- actual - result$e$base[1, ] # recover 1-step ahead base forecast

      # Winkler score for base model
      result_winklers_80[[model]][i, ] <- vectorise_winkler(
        base_fc, sqrt(diag(W1_hats[[model]])), actual, 80
      )
      result_winklers_95[[model]][i, ] <- vectorise_winkler(
        base_fc, sqrt(diag(W1_hats[[model]])), actual, 95
      )
      # CRPS for base model
      result_crps[[model]][i, ] <- vectorise_crps(
        base_fc, sqrt(diag(W1_hats[[model]])), actual
      )

    } else {
      # obtain mapping G
      if (model %in% c("ols", "ols_shr")) {
        G <- solve(t(S) %*% S) %*% t(S)
      } else {
        P <- t(S) %*% solve(W1_hats[[model]])
        G <- solve(P %*% S) %*% P
      }
      # get reconciled forecast and covariance
      if (model == "ols_shr") {
        # ols_shr uses ols reconciled forecast
        y_recon <- actual - result$e[["ols"]][1, ]
      } else {
        y_recon <- actual - result$e[[model]][1, ]
      }
      W1_recon <- S %*% G %*% W1_hats[[model]] %*% t(G) %*% t(S)

      # Winkler score for reconciled model
      result_winklers_80[[model]][i, ] <- vectorise_winkler(
        mu = y_recon, sd = sqrt(diag(W1_recon)), actual, 80
      )
      result_winklers_95[[model]][i, ] <- vectorise_winkler(
        mu = y_recon, sd = sqrt(diag(W1_recon)), actual, 95
      )
      # CRPS for reconciled model
      result_crps[[model]][i, ] <- vectorise_crps(
        mu = y_recon, sd = sqrt(diag(W1_recon)), actual
      )
    }
  }
  cat("Done", i, "\n")
}

# remove 19th row
nrow(result_winklers_95[[1]])
result_winklers_80 <- lapply(result_winklers_80, function(mat) mat[-19, ])
result_winklers_95 <- lapply(result_winklers_95, function(mat) mat[-19, ])
result_crps <- lapply(result_crps, function(mat) mat[-19, ])

# saveRDS(result_winklers_80, "tourism/job/results/result_winklers_80.rds")
# saveRDS(result_winklers_95, "tourism/job/results/result_winklers_95.rds")
# saveRDS(result_crps, "tourism/job/results/result_crps.rds")
```

### Inspect OLS_shr

```{r}
all.equal(W1_hats[["ols_shr"]], W1_hats[["mint_shr"]])
all.equal(diag(W1_hats[["ols"]]), diag(W1_hats[["ols_shr"]]))

base_cov <- compute_cov_matrix(resid, T)
shr_cov <- shrinkage_est(resid)

G <- solve(t(S) %*% S) %*% t(S)
W1_recon_ols <- S %*% G %*% base_cov %*% t(G) %*% t(S)
W1_recon_ols_shr <- S %*% G %*% shr_cov$cov %*% t(G) %*% t(S)

W1_recon_ols_diag <- S %*% G %*% diag(diag(base_cov)) %*% t(G) %*% t(S)

all.equal(shr_cov$cov, shr_cov$lambda * diag(diag(base_cov)) + (1 - shr_cov$lambda) * base_cov) # TRUE
all.equal(
  W1_recon_ols_shr, 
  shr_cov$lambda * S %*% G %*% diag(diag(base_cov)) %*% t(G) %*% t(S) + (1 - shr_cov$lambda) * W1_recon_ols
) # TRUE 

P <- t(S) %*% solve(W1_hats[["mint_shr"]])
G <- solve(P %*% S) %*% P
W1_recon_mint_shr <- S %*% G %*% W1_hats[["mint_shr"]] %*% t(G) %*% t(S)

P <- t(S) %*% solve(W1_hats[["mint_n"]])
G <- solve(P %*% S) %*% P
W1_recon_mint_n <- S %*% G %*% W1_hats[["mint_n"]] %*% t(G) %*% t(S)

# inspect variance shrinkage for ols
tibble(
  series = colnames(W1_recon_ols),
  ols = diag(W1_recon_ols), 
  ols_shr = diag(W1_recon_ols_shr),
  mint_shr = diag(W1_recon_mint_shr),
  mint_n = diag(W1_recon_mint_n)
) |>
  mutate(
    diff = mint_shr - mint_n,
    pct_shrink = diff / mint_shr * 100
    # diff = ols_shr - ols,
    # pct_shrink = diff / ols * 100    
  ) |>
  arrange(desc(pct_shrink)) |>
  # cap at 100%
  # mutate(pct_shrink = pmin(pct_shrink, 100)) |>
  # ploot
  ggplot(aes(x = reorder(series, pct_shrink), y = pct_shrink)) +
    geom_col() +
    coord_flip() +
    labs(x = "Series", y = "% reduction in variance",
         title = "% change in variance by shrinkage for OLS (var ols_shr - var ols)",
         subtitle = "iter 133") +
    theme_minimal() +
    theme(axis.text.y = element_blank())
```

## Wrangle and plots
```{r}
library(stringr)

result_winklers_80 <- readRDS("tourism/job/results/result_winklers_80_new.rds")
result_winklers_95 <- readRDS("tourism/job/results/result_winklers_95_new.rds")
result_crps <- readRDS("tourism/job/results/result_crps_new.rds")

get_score_df <- function(result_score){
  score_df <- result_score |> 
    transform_sim_MSE(F) |> 
    # change column name "h" to "iter", "MSE" to "score"
    rename(
      iter = h, 
      score = MSE
    )
  # wrangle
  {
    # add level
    score_df <- score_df %>% 
      mutate(
        level = level_map[series] %||% NA_character_,
        # %||% is just “if lookup returns NULL, fall back to NA
        level = factor(
          level,
          levels = desired_order,
          labels = str_replace_all(desired_order, "_", " ")  # replace "_" with " "
        )
      )
    # filter last 3 years
    score_df <- score_df %>%
      filter(iter <= 97) # keep only the first 97 iterations
    # average of % improvements per series
    score_df <- score_df |>
      group_by(series, iter) |>
      mutate(
        base_score = score[.model == "base"]
      ) |>
      ungroup() |>
      mutate(pct_change_per_series = (score - base_score) / base_score * 100)
  
    encode_recon_models(score_df) |> 
      select(-method_raw, -shape_lab, -linetype_lab, -variant_type)
  }
}
score_df <- get_score_df(result_winklers_80) |> mutate(rule = "W80")
score_df <- rbind(score_df, get_score_df(result_winklers_95) |> mutate(rule = "W95"))
score_df <- rbind(score_df, get_score_df(result_crps) |> mutate(rule = "CRPS"))


```

```{r pct over average}
# # winklers improvements per model
# score_label <- "CRPS"
# score_df |>
#   filter(rule == score_label) |>
#   group_by(family, model_label) |>
#   summarise(
#     score = mean(score),
#     base_score = mean(base_score),
#     pct_change = (score - base_score) / base_score * 100
#   ) |> 
#   filter(model_label != "Base") |>
#   ggplot(aes(x = model_label, y = pct_change, fill = family)) +
#     geom_col() +
#     labs(x = "Model", y = "% improvements",
#          title = paste("Average of % relative improvements in", score_label, "compared to Base"),
#          subtitle = "Interpret: negative values indicate improvement. Pct over Avg") +
#     scale_fill_manual(
#       name = "Family",
#       values = c("OLS" = "#d1d400ff", "MinT-S" = "#00c086ff", "MinT-N" = "#9500c2ff")
#     ) +
#     theme_minimal()

# # winklers improvements per model per level
# score_df |>
#   group_by(series, iter) |>
#   mutate(
#     base_score = score[.model == "base"]
#   ) |>
#   ungroup() |>
#   group_by(.model, level) |>
#   summarise(
#     score = mean(score),
#     base_score = mean(base_score),
#     pct_change = (score - base_score) / base_score * 100
#   ) |> 
#   ggplot(aes(x = .model, y = pct_change, fill = .model)) +
#     geom_col(position = "dodge") +
#     labs(x = "Level", y = "% improvements",
#          title = "% relative improvements in CRPS compared to Base",
#          subtitle = "Interpret: negative values mean improvement") +
#     facet_wrap(~ level, ncol=2, scales = "free_y") +
#     theme_minimal()
```

## Average of % improvements
```{r}
# score_label <- "W95"
# score_df |> 
#   filter(rule == score_label) |>
#   group_by(family, model_label) |> 
#   summarise(
#     pct_change_avg = mean(pct_change_per_series),
#     # capped at 10%
#     pct_change_avg = pmin(pct_change_avg, 10),
#     capped = ifelse(pct_change_avg >= 10, 1, 0)
#   ) |> 
#   filter(model_label != "Base") |>
#   ggplot(aes(x = model_label, y = pct_change_avg, fill = family)) +
#     geom_col() +
#     labs(x = "Model", y = "% improvements",
#          title = paste("Average of % relative improvements in", score_label, "compared to Base"),
#          subtitle = "Interpret: negative values indicate improvement. Avg over pct") +
#     # labels on top of bars if capped
#     geom_text(aes(label = ifelse(capped == 1, "> 10%", "")), vjust = -0.5) +
#     scale_fill_manual(
#       name = "Family",
#       values = c(
#         "OLS"    = "#d1d400ff",  # black
#         "MinT-S" = "#00c086ff",  # teal (colorblind-friendly)
#         "MinT-N" = "#9500c2ff"   # purple
#       )
#     ) +
#     theme_minimal()

# # per level, inconsistent calculation
# score_label <- "W80"
# score_df |> 
#   filter(rule == score_label) |>
#   group_by(family, model_label, pc_k, level) |> 
#   summarise(
#     pct_change_avg = mean(pct_change_per_series)
#     # capped at 10%
#     # pct_change_avg = pmin(pct_change_avg, 10),
#     # capped = ifelse(pct_change_avg >= 10, 1, 0)
#   ) |> 
#   filter(model_label != "Base") |>
#   mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) %>%
#   # ggplot
#   ggplot(aes(x = model_label, y = pct_change_avg, fill = family, alpha = pc_k)) +
#     geom_col(color = "black", size = 0.5) +
#     labs(x = "Level", y = "% improvements",
#          title = "Winkler score 80% by level",
#         #  title = paste("Average of % relative improvements in", score_label, "compared to Base"),
#         #  subtitle = "Interpret: negative values mean improvement. Avg over pct"
#         ) +
#     facet_wrap(~ level, ncol=2, scales = "free_y") +
#     # markers on top of bars if capped, not using texts
#     # geom_point(data = . %>% filter(capped == 1), aes(x = model_label, y = 10 + 0.5), shape = 8, size = 3, color = "red") +
#     scale_fill_manual(
#       name = "Family",
#       values = c(
#         "OLS"    = "#d1d400ff",  # black
#         "MinT-S" = "#00c086ff",  # teal (colorblind-friendly)
#         "MinT-N" = "#9500c2ff"   # purple
#       )
#     ) +
#     scale_alpha_manual(values = c("0" = 1, "1" = 0.7, "2" = 0.4), guide = "none") +
#     theme_minimal() +
#     # rotate the x axis labels
#     theme(axis.text.x = element_text(angle = 45, hjust = 0.7))


# Consistent plotting:
# average across series per iteration -> compute % improv per iter -> average across iter
score_label <- "CRPS"
score_df %>%
  filter(rule == score_label) %>%
  group_by(family, model_label, pc_k, iter) %>%
  summarise(
    score = mean(score),
    base_score = mean(base_score),
    pct_change = (base_score - score) / base_score * 100,
    .groups = "drop_last"
  ) %>%
  ungroup() %>%
  group_by(family, model_label, pc_k) %>%
  summarise(
    pct_change_avg = pmin(mean(pct_change), 10),   # cap at 10
    capped = as.integer(pct_change_avg >= 10),
    .groups = "drop"
  ) %>%
  filter(model_label != "Base", model_label != "OLS-S") %>%
  mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) %>%
  # ggplot
  ggplot(aes(x = model_label, y = pct_change_avg,
             fill = family, alpha = pc_k)) +
    geom_col(color = "black", size = 0.5) +
    # geom_text(aes(label = ifelse(capped == 1, "> 10%", "")), vjust = -0.5) +
    recon_fill_scale +
    scale_alpha_manual(values = c("0" = 1, "1" = 0.6, "2" = 0.3), guide = "none") +
    labs(
      x = "Model", y = "% improvements",
      title = paste(score_label)
    ) +
    theme_minimal(base_size = 12) +
    theme(axis.text.x = element_text(angle = 25, hjust = 0.6))
```

```{r radar}
#radar chart

# # ----- inconsistent % improv -----
# radar_df <- score_df |> 
#   filter(.model %in% c("mint_shr", "mint_n", "mint_shr_pc_K1", "mint_n_pc_K1")) |>
#   group_by(.model, rule) |>
#   summarise(pct_change_avg = mean(pct_change_per_series), .groups = "drop") |>
#   pivot_wider(names_from = rule, values_from = pct_change_avg) |>
#   column_to_rownames(".model")

# radar_df <- cbind(
#   radar_df,
#   Energy = energy_df |> 
#     group_by(.model) |> 
#     summarise(
#       mean_score = mean(score),
#       pct_change_avg = mean(pct_change_per_series)
#     ) |> 
#     filter(.model %in% c("mint_shr", "mint_n", "mint_shr_pc_K1", "mint_n_pc_K1")) |> 
#     pull(pct_change_avg)
# )

# ----- consistent % improv -----
radar_df <- score_df |> 
  filter(.model %in% c("ols", "mint_shr", "mint_n", "mint_shr_pc_K1", "mint_n_pc_K1")) |>
  # average across series per iteration & compute % improv per iter
  group_by(model_label, rule, iter) |>
  summarise(
    score = mean(score),
    base_score = mean(base_score),
    pct_change = (score - base_score) / base_score * 100
  ) |>
  ungroup() |>
  # average across iter
  group_by(model_label, rule) |>
  summarise(
    pct_change_avg = mean(pct_change)
  ) |>
  ungroup() |>
  filter(model_label != "Base") |>
  pivot_wider(names_from = rule, values_from = pct_change_avg) |>
  column_to_rownames("model_label")

radar_df <- cbind(
  radar_df,
  Energy = energy_df |> 
    filter(.model %in% c("ols", "mint_shr", "mint_n", "mint_shr_pc_K1", "mint_n_pc_K1")) |> 
    group_by(model_label) |> 
    summarise(
      mean_score = mean(score),
      pct_change_avg = mean(pct_change_per_series)
    ) |> 
    pull(pct_change_avg)
)




radar_df <- -radar_df # flip sign so larger is better outward

{# --- 2) Add required max/min rows for fmsb::radarchart ---
maxs <- apply(radar_df, 2, max, na.rm = TRUE)
mins <- apply(radar_df, 2, min, na.rm = TRUE)
mins <- pmin(mins, 0) # ensure min is at most 0

# pad the scale a bit so polygons don’t touch edges
pad  <- 0.01 * (maxs - mins)
scale_top <- maxs + pad
scale_bot <- mins - pad

plot_df <- rbind(scale_top, scale_bot, radar_df)

# --- 3) Colors (one per method, in row order) ---
cols <- c("#7b7b7bff","#1B9E77", "#6A51A3", "#66A61E", "#E6AB02")[seq_len(nrow(radar_df))]

# --- 4) Draw radar chart ---
radarchart(
  plot_df,
  axistype = 1,
  pcol  = cols,
  pfcol = scales::alpha(cols, 0.20),
  plwd  = 2,
  plty  = 1,
  cglcol = "grey80", cglty = 1, cglwd = 0.8,
  axislabcol = "grey30",
  vlcex = 0.9
)

legend("topright", legend = rownames(radar_df),
       col = cols, lty = 1, lwd = 2, bty = "n", cex = 0.9)
# title
title(main = "Average of % relative improvements compared to Base")
# subtitle
mtext("Interpret: larger values indicate better performance", side = 3, line = 0.5, cex = 0.8)
}

make_radar <- function(plot_df, radar_df, cols) {
  fmsb::radarchart(
    plot_df,
    axistype = 1,
    pcol  = cols,
    pfcol = scales::alpha(cols, 0.20),
    plwd  = 2,
    plty  = 1,
    cglcol = "grey80", cglty = 1, cglwd = 0.8,
    axislabcol = "grey30",
    vlcex = 0.9
  )
  legend("topright", legend = rownames(radar_df),
         col = cols, lty = 1, lwd = 2, bty = "n", cex = 0.9)

  recordPlot()  # <- returns a recordedplot
}
plot7 <- make_radar(plot_df, radar_df, cols)

```


## lolipop plots
```{r}
library(tidytext)
pef_model <- "mint_n_pc_K1"
score_label <- "CRPS"

plot_df <- score_df |> 
  filter(rule == score_label) |>
  group_by(series, level, .model) |> 
  # # % improv -> avg
  # summarise(pct_change_avg = mean(pct_change_per_series), .groups = "drop") |>
  # avg -> % improv
  summarise(
    score = mean(score),
    base_score = mean(base_score),
    pct_change_avg = (score - base_score) / base_score * 100,
    .groups = "drop"
  ) |>
  # cap at 30%
  mutate(pct_change_avg = pmin(pct_change_avg, 30)) |> 
  # sort series by pct_change_avg of mint_n_pc_K1
  # mutate(series = fct_reorder(series, pct_change_avg[.model == "mint_n_pc_K1"])) |>  
  # filter(level == "Region") |>
  filter(!grepl("K2|ols_shr", .model)) |> 
  # 4 facets
  mutate(level_group = case_when(
    level %in% c("Australia", "Australia by Purpose", "State", "State by Purpose") ~ "1.High levels",
    level %in% c("Zone", "Zone by Purpose") ~ "2.Zone & Zone by Purpose",
    level == "Region" ~ "3.Region",
    level == "Region by Purpose" ~ "4.Region by Purpose",
    TRUE ~ NA_character_
  )) |>
  # collapse to 2 facets
  mutate(level_group = case_when(
    level_group %in% c("1.High levels", "2.Zone & Zone by Purpose") ~ "1.High levels",
    level_group %in% c("3.Region", "4.Region by Purpose") ~ "2.Region and Region by Purpose",
  )) |>
  group_by(level_group, series) |>
  mutate(order_key = pct_change_avg[.model == pef_model][1]) |>
  ungroup() |>
  mutate(order_key = if_else(is.na(order_key), -Inf, order_key),
         series_ord = reorder_within(series, order_key, level_group, .desc = TRUE))


ggplot(plot_df, aes(x = series_ord, y = pct_change_avg)) +
  geom_segment(aes(xend = series_ord, yend = 0), color = "grey") +
  geom_point(aes(color = .model, shape = .model), size = 2) +
  coord_flip() +
  facet_wrap(~ level_group, ncol = 2, scales = "free_y") + # free_y drops unused levels per facet
  scale_x_reordered() +                                    # remove the internal suffix used by reorder_within
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        legend.position = "bottom") +
  labs(x = "Series", y = "% improvements",
       title = paste("Average of % relative improvements in", score_label, "compared to Base"),
       subtitle = "Negative values mean improvement; values ≥ 30% are capped at 30%")
```


## Get Energy Score

Need sampling to approximate the energy score.
To ensure coherency, we sample from the reconciled distribution of the bottom-level series, then aggregate up to obtain all levels.

mu_b = G * mu
W_b = G * W * G^T
b_sample ~ N(mu_b, W_b)
y_sample = S * b_sample

Calculate energy score from y_samples and actuals

```{r helpers}
coherent_draws <- function(mu_base, Sigma_base, S, G, m) {
  # mu: vector of base forecast means (all series)
  # Sigma: covariance matrix of base forecast (all series)
  
  mu_bot <- G %*% mu_base
  Sigma_bot <- G %*% Sigma_base %*% t(G)
  
  b_samples <- MASS::mvrnorm(m, mu_bot, Sigma_bot) # m x p_bottpm
  y_samples <- t(S %*% t(b_samples))           # m x p
  return(y_samples)
}

energy_score_from_samples <- function(samples, actual) {
  m <- nrow(samples)
  term1 <- mean(sqrt(rowSums(
    (sweep(samples, 2, actual, "-"))^2
  )))
  term2 <- mean(sqrt(rowSums(
    (samples[sample(1:m, m, replace = TRUE), ] - samples[sample(1:m, m, replace = TRUE), ])^2
  )))
  return(term1 - 0.5 * term2)
}
```

```{r get energy score}
library(distributional)

M <- length(result_list_full)
model_names <- all_model_names[!grepl("K5|K10|K20", all_model_names)] # remove pc models
model_names <- c(model_names, "base_shr", "ols_shr") # add base_shr ols_shr FOR MULTIVARIATE ONLY

#   row - CV iterations
#   col - models
result_energy <- matrix(0, M, length(model_names),
  dimnames = list(1:M, model_names)
)

# Get actual data
y <- visnights_full |> 
  as_tibble() |> 
  arrange(State, Region) |>
  left_join(row_names, by = c("State", "Zone", "Region", "Purpose")) |>
  select(name, Nights, Month) |>
  pivot_wider(names_from = name, values_from = Nights) |>
  select(-Month) |>
  as.matrix()
y <- y[, rownames(S)]

start_date <- seq_dates$start[1]
m <- 10000 # number of samples

for (i in 1:M) {
  
  if (i == 19) next # iteration 19 has error
  result <- result_list_full[[i]]
  result$e <- flatten_e_list(result$e) # flatten the list of errors
  resid <- result$resid

  actual <- y[seq_dates$end[i] + 1 - start_date + 1, ] # 1-step ahead actuals

  # Recover a list of W1_hat for each model
  W1_hats <- list()
  W1_hats[["base"]] <- nearPD(cov(resid))$mat |> as.matrix() # sample variance of 1-step-ahead residuals as a proxy
  W1_hats[["ols"]] <- W1_hats[["base"]]

  W1_hats[["mint_shr"]] <- shrinkage_est(resid, result$W_shr[1])$cov
  W1_hats[["mint_n"]] <- novelist_est(resid, result$W_n["delta", 1], result$W_n["lambda", 1])$cov
  rownames(W1_hats[["mint_n"]]) <- colnames(W1_hats[["mint_n"]]) <- rownames(S)
  # pc models
  W1_hats[["mint_shr_pc_K1"]] <- shrinkage_pc_est(resid, 1, result$W_shr[2])$cov
  W1_hats[["mint_shr_pc_K2"]] <- shrinkage_pc_est(resid, 2, result$W_shr[3])$cov
  W1_hats[["mint_n_pc_K1"]] <- novelist_pc_est(resid, 1, result$W_n["delta", 2], result$W_n["lambda", 2])$cov
  W1_hats[["mint_n_pc_K2"]] <- novelist_pc_est(resid, 2, result$W_n["delta", 3], result$W_n["lambda", 3])$cov

  W1_hats[["base_shr"]] <- shrinkage_est(resid)$cov   # FOR MULTIVARIATE ONLY
  W1_hats[["ols_shr"]] <- W1_hats[["base_shr"]]
    
  for (model in model_names) {

    if (model %in% c("base", "base_shr")) {
      base_fc <- actual - result$e$base[1, ] # recover 1-step ahead base forecast

      # Energy score for base model
      samples <- MASS::mvrnorm(m, base_fc, W1_hats[[model]])
      result_energy[i, model] <- energy_score_from_samples(samples, actual)

    } else {
      # obtain mapping G
      if (model %in% c("ols", "ols_shr")) {
        G <- solve(t(S) %*% S) %*% t(S)
      } else {
        P <- t(S) %*% solve(W1_hats[[model]])
        G <- solve(P %*% S) %*% P
      }
      # Energy score for reconciled model
      samples <- coherent_draws(base_fc, W1_hats[[model]], S, G, m)
      result_energy[i, model] <- energy_score_from_samples(samples, actual)
    }
  }
  cat("Done", i, "\n")
}
```

```{r wrangle energy score}
# saveRDS(result_energy, "tourism/job/results/result_energy_10k.rds")

readRDS("tourism/job/results/result_energy_10k.rds") -> result_energy
# remove 19th row
if (all(result_energy[19, ] == 0)) {
  cat("Removing 19th row\n")
  result_energy <- result_energy[-19, ]
}

{
  energy_df <- result_energy |> 
    as_tibble(rownames = "iter") |>
    pivot_longer(-iter, names_to = ".model", values_to = "score") |>
    mutate(iter = as.integer(iter))
  # filter last 3 years
  energy_df <- energy_df |> 
    filter(iter <= 97 - 1) # keep only the first 97 iterations
  # pct change
  energy_df <- energy_df |> 
    group_by(iter) |>
    mutate(
      base_score = score[.model == "base"],
      pct_change_per_series = (base_score - score) / base_score * 100 # positive means improvement
    )
  energy_df <- encode_recon_models(energy_df)
}
```

## Plots

```{r}
# overall energy score per model
energy_df |> 
  group_by(family, model_label, pc_k) |> 
  summarise(
    pct_change_avg = mean(pct_change_per_series)
  ) |>
  mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) |> 
  filter(! grepl("Ba|OLS-S", model_label)) |>
  ggplot(aes(x = model_label, y = pct_change_avg, fill = family, alpha = pc_k)) +
    geom_col(color = "black", size = 0.5) +
    recon_fill_scale +
    scale_alpha_manual(values = c("0" = 1, "1" = 0.7, "2" = 0.4), guide = "none") +
    labs(x = "Model", y = "% improvements"
        #  title = "Energy Score"
        #  title = "Average of % relative improvements in Energy Score compared to Base",
        #  subtitle = "Negative values indicate improvement. Avg over pct. Test set ends 2016"
        ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 25, hjust = 0.6))


# # compute average energy score then compute pct change
# energy_df |> 
#   group_by(family, model_label) |> 
#   summarise(
#     mean_score = mean(score),
#     mean_base_score = mean(base_score),
#     pct_change_avg = (mean_score - mean_base_score) / mean_base_score * 100
#   ) |>
#   filter(model_label != "Base") |>
#   ggplot(aes(x = model_label, y = pct_change_avg, fill = family)) +
#     geom_col() +
#     labs(x = "Model", y = "% improvements",
#          title = "Average of % relative improvements in Energy Score compared to Base",
#          subtitle = "Negative values indicate improvement. Avg over pct. Test set ends 2016") +
#     scale_fill_manual(
#       name = "Family",
#       values = c(
#         "Base"   = "#7A7A7A",  # grey
#         "OLS"    = "#d1d400ff",  # black
#         "MinT-S" = "#00c086ff",  # teal (colorblind-friendly)
#         "MinT-N" = "#9500c2ff"   # purple
#       )
#     ) +
#     theme_minimal()

```


## Inspect MinT-Shr worse performance on W95

```{r}
score_df |> group_by(iter, .model) |> summarise(score = mean(score), base_score=mean(base_score), pct_change=(base_score-score)/base_score) |> arrange(desc(pct_change))
```

```{r}
i <- 42
result <- result_list_full[[i]]
e <- result$e |> flatten_e_list()
resid <- result$resid

# Get actual data
y <- visnights_full |> 
  as_tibble() |> 
  arrange(State, Region) |>
  left_join(row_names, by = c("State", "Zone", "Region", "Purpose")) |>
  select(name, Nights, Month) |>
  pivot_wider(names_from = name, values_from = Nights) |>
  select(-Month) |>
  as.matrix()
y <- y[, rownames(S)]
actual <- y[seq_dates$end[i] + 1 - start_date + 1, ] # 1-step ahead actuals

W1_base <- compute_cov_matrix(resid, T)
y_base <- actual - result$e[["base"]][1, ]

# # MinT-S
# W1_recon <- shrinkage_est(resid, result$W_shr[1])$cov
# y_recon <- actual - result$e[["mint_shr"]][1, ]
# MinT-N(PC1)
W1_recon <- novelist_pc_est(resid, 1, result$W_n["delta", 2], result$W_n["lambda", 2])$cov
y_recon <- actual - result$e$mint_n_pc$K1[1, ]
P <- t(S) %*% solve(W1_recon)
G <- solve(P %*% S) %*% P

# # OLS
# W1_recon <- W1_base
# y_recon <- actual - result$e[["ols"]][1, ]
# G <- solve(t(S) %*% S) %*% t(S)
W1_recon <- S %*% G %*% W1_recon %*% t(G) %*% t(S)

var_series <- tibble(
  series = colnames(W1_recon),
  base_fc = y_base,
  recon_fc = y_recon,
  var_base = diag(W1_base), 
  var_recon = diag(W1_recon),
  diff = var_recon - var_base,
  pct_change = diff / var_base * 100 # negative means reduction in variance
)
# plot pct change vertically
var_series %>%
  arrange(pct_change) %>%
  mutate(series = factor(series, levels = series)) %>%
  ggplot(aes(x = series, y = pct_change)) +
    geom_col() +
    coord_flip() +
    theme_minimal() +
    theme(axis.text.y = element_blank())
any(var_series$pct_change > 0)

# look at the bounds 95%
bound_series <- tibble(
  series = colnames(W1_recon),
  base_lower = qnorm(0.025, mean = actual - result$e[["base"]][1, ], sd = sqrt(diag(W1_base))),
  base_upper = qnorm(0.975, mean = actual - result$e[["base"]][1, ], sd = sqrt(diag(W1_base))),
  mint_shr_lower = qnorm(0.025, mean = actual - result$e[["mint_shr"]][1, ], sd = sqrt(diag(W1_recon))),
  mint_shr_upper = qnorm(0.975, mean = actual - result$e[["mint_shr"]][1, ], sd = sqrt(diag(W1_recon)))
) %>%
  mutate(
    base_width = base_upper - base_lower,
    mint_shr_width = mint_shr_upper - mint_shr_lower,
    diff_width = mint_shr_width - base_width,
    pct_change_width = diff_width / base_width * 100 # negative means reduction in width
  )

# look at the WS95 of 42 iter
temp <- score_df |> 
  filter(
    iter == i, 
    rule == "W95",
    .model %in% c("mint_shr")
  ) |>
  # plot diff score vertically
  mutate(diff = score - base_score) |> 
  arrange(desc(diff)) |> 
  mutate(series = factor(series, levels = series))

temp |> 
  ggplot(aes(x = series, y = diff)) +
    geom_col() +
    coord_flip() +
    theme_minimal() +
    theme(axis.text.y = element_blank())

temp[1,]
var_series[560,]
bound_series[560,]
actual[560]


manual_compute <- bound_series[560,"base_width"] |> pull()
score_df |> 
  filter(
    rule == "W95",
    .model %in% c("mint_shr")
  )  |> filter(abs(base_score - manual_compute) < 1e-6)

manual_compute <- bound_series[560,"mint_shr_width"] |> pull()
score_df |> 
  filter(
    rule == "W95",
    .model %in% c("mint_shr")
  )  |> filter(abs(score - manual_compute) < 1e-6)
```


### Calculating coverage
```{r loop calculate coverage}
M <- length(result_list)
coverage <- 0.8
lower_q <- (1 - coverage) / 2; upper_q <- 1 - lower_q
model_names <- c("base", "ols", "mint_shr", "mint_n", "mint_shr_pc_K1", "mint_n_pc_K1")

#   row - series
#   col - models
result_coverage <- matrix(0, ncol = length(model_names), nrow = nrow(S),
  dimnames = list(rownames(S), model_names)
)

# Get actual data
y <- visnights_full |> 
  as_tibble() |> 
  arrange(State, Region) |>
  left_join(row_names, by = c("State", "Zone", "Region", "Purpose")) |>
  select(name, Nights, Month) |>
  pivot_wider(names_from = name, values_from = Nights) |>
  select(-Month) |>
  as.matrix()
y <- y[, rownames(S)]

start_date <- seq_dates$start[1]

for (i in 1:M) {
  
  result <- result_list_full[[i]]
  result$e <- flatten_e_list(result$e) # flatten the list of errors
  resid <- result$resid

  actual <- y[seq_dates$end[i] + 1 - start_date + 1, ] # 1-step ahead actuals

  # Recover a list of W1_hat for each model
  W1_hats <- list()
  W1_hats[["base"]] <- compute_cov_matrix(resid, T) # sample variance of 1-step-ahead residuals as a proxy
  W1_hats[["ols"]] <- W1_hats[["base"]]

  W1_hats[["mint_shr"]] <- shrinkage_est(resid, result$W_shr[1])$cov
  W1_hats[["mint_n"]] <- novelist_est(resid, result$W_n["delta", 1], result$W_n["lambda", 1])$cov
  rownames(W1_hats[["mint_n"]]) <- colnames(W1_hats[["mint_n"]]) <- rownames(S)

  # pc models
  W1_hats[["mint_shr_pc_K1"]] <- shrinkage_pc_est(resid, 1, result$W_shr[2])$cov
  W1_hats[["mint_n_pc_K1"]] <- novelist_pc_est(resid, 1, result$W_n["delta", 2], result$W_n["lambda", 2])$cov
  
  for (model in model_names) {

    if (model == "base") {
      base_fc <- actual - result$e$base[1, ] # recover 1-step ahead base forecast

      # coverage for base model
      # add 1 if actual is within interval
      lower <- qnorm(lower_q, mean = base_fc, sd = sqrt(diag(W1_hats[[model]])))
      upper <- qnorm(upper_q, mean = base_fc, sd = sqrt(diag(W1_hats[[model]])))
      result_coverage[, model] <- result_coverage[, model] + (actual >= lower & actual <= upper)

    } else {
      # obtain mapping G
      if (model == "ols") {
        G <- solve(t(S) %*% S) %*% t(S)
      } else {
        P <- t(S) %*% solve(W1_hats[[model]])
        G <- solve(P %*% S) %*% P
      }
      # get reconciled forecast and covariance
      y_recon <- actual - result$e[[model]][1, ]
      W1_recon <- S %*% G %*% W1_hats[[model]] %*% t(G) %*% t(S)

      # coverage for reconciled model
      lower <- qnorm(lower_q, mean = y_recon, sd = sqrt(diag(W1_recon)))
      upper <- qnorm(upper_q, mean = y_recon, sd = sqrt(diag(W1_recon)))
      result_coverage[, model] <- result_coverage[, model] + (actual >= lower & actual <= upper)
    }
  }
  cat("Done", i, "\n")
}

result_coverage <- result_coverage/M 
```

```{r plotting coverage}
library(tidytext)
library(stringr)

# horizontal lolipop plots of coverage, faceted by level
result_coverage <- readRDS("tourism/job/results/result_coverage95.rds")

plot_df <- as_tibble(result_coverage, rownames = "series") |> 
  pivot_longer(-series, names_to = ".model", values_to = "coverage") |>
  left_join(row_names, by = c("series" = "name")) |>
  mutate(
    level = level_map[series] %||% NA_character_,
    # %||% is just “if lookup returns NULL, fall back to NA
    level = factor(
      level,
      levels = desired_order,
      labels = str_replace_all(desired_order, "_", " ")  # replace "_" with " "
    )
  ) |>
  # 4 facets
  mutate(level_group = case_when(
    level %in% c("Australia", "Australia by Purpose", "State", "State by Purpose") ~ "1.High levels",
    level %in% c("Zone", "Zone by Purpose") ~ "2.Zone & Zone by Purpose",
    level == "Region" ~ "3.Region",
    level == "Region by Purpose" ~ "4.Region by Purpose",
    TRUE ~ NA_character_
  )) |>
  # collapse to 2 facets
  mutate(level_group = case_when(
    level_group %in% c("1.High levels", "2.Zone & Zone by Purpose") ~ "1.High levels",
    level_group %in% c("3.Region", "4.Region by Purpose") ~ "2.Region and Region by Purpose",
  )) |>
  group_by(level_group, series) |>
  mutate(order_key = coverage[.model == "mint_n_pc_K1"][1]) |>
  ungroup() |>
  mutate(order_key = if_else(is.na(order_key), -Inf, order_key),
         series_ord = reorder_within(series, order_key, level_group, .desc = TRUE))

ggplot(plot_df, aes(x = series_ord, y = coverage)) +
  # geom_segment(aes(xend = series_ord, yend = 0), color = "grey") +
  geom_point(aes(color = .model, shape = .model), size = 2) +
  facet_wrap(~ level_group, ncol = 1, scales = "free") + # free_y drops unused levels per facet
  geom_hline(yintercept = coverage, linetype = "dashed", color = "black") + # draw line for coverage
  # change y axis scale to 0.8 to 1
  scale_y_continuous(limits = c(0.45, 1), breaks = seq(0.55, 0.95, by = 0.1)) +
  scale_x_reordered() + # remove the internal suffix used by reorder_within
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(x = "Series", y = "Empirical Coverage",
       title = "Empirical coverage of 80% prediction intervals")

# top 20 worst coverage of mint_shr
plot_df |> 
  pivot_wider(names_from = .model, values_from = coverage) |>
  arrange(desc(mint_shr)) |>
  select(series, level, eval(model_names)) |>
  print(n=20)

# average coverage per model per level
coverage <- 0.95
plot_df |> 
  group_by(level, .model) |> 
  summarise(mean_coverage = mean(coverage)) |> 
  encode_recon_models() |> 
  mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) |> 
  ggplot(aes(x = model_label, y = mean_coverage, fill = family, alpha = pc_k)) +
    geom_col(color = "black", size = 0.5) +
    scale_alpha_manual(values = c("0" = 1, "1" = 0.7, "2" = 0.4), guide = "none") +
    labs(x = "Model", y = "Empirical Coverage",
         title = "Empirical coverage of 95% prediction intervals by level") +
    geom_hline(yintercept = 0.95, linetype = "dashed", color = "black") + # draw line for coverage
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    recon_fill_scale +
    theme_minimal() +
    # rotate the x axis labels
    theme(axis.text.x = element_text(angle = 45, hjust = 0.7))
  
```

```{r}
# plot WS95 by level
score_label <- "W95"

score_df |> 
  filter(rule == score_label) |> 
  group_by(family, model_label, pc_k, level) |> 
  summarise(
    score = mean(score),
    base_score = mean(base_score),
    pct_change = (base_score - score) / base_score *100
  ) |> 
  filter(! grepl("Ba|OLS-S|PC2", model_label)) |>
  mutate(pc_k = ifelse(is.na(pc_k), "0", as.character(pc_k))) |> 
  # ggplot
  ggplot(aes(x = model_label, y = pct_change, fill = family, alpha = pc_k)) +
    geom_col(color = "black", size = 0.5) +
    scale_alpha_manual(values = c("0" = 1, "1" = 0.7, "2" = 0.4), guide = "none") +
    labs(x = "Level", y = "% improvements",
         title = "Winkler score 95% by level"
        #  title = paste("Average of % relative improvements in", score_label, "compared to Base"),
        #  subtitle = "Interpret: positive values indicate improvement. Avg over pct"
        ) +
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    recon_fill_scale +
    theme_minimal() +
    # rotate the x axis labels
    theme(axis.text.x = element_text(angle = 45, hjust = 0.75))
```

```{r}
# distributions of errors
high_levels <- score_df |> 
  filter(level %in% c("Australia", "State", "Australia by Purpose")) |> pull(series) |> unique()
y[(seq_dates$end[1] + 1 - start_date + 1):nrow(y),high_levels]

e_df <- matrix(NA, nrow = M, ncol = nrow(S),
  dimnames = list(NULL, rownames(S))
)
for (i in 1:M) {
  result <- result_list_full[[i]]
  result$e <- flatten_e_list(result$e) # flatten the list of errors
  # mint_shr
  # e_df[i, ] <- result$e$mint_shr[1, ]
  # ols
  e_df[i, ] <- result$e$ols[1, ]
  # mint_n_pc_K1
  # e_df[i, ] <- result$e$mint_n_pc_K1[1, ]
}

# same historgram but with 95% bounds vertical lines for each series, bounds got from the errors
bounds <- t(apply(e_df, 2, function(x) quantile(x, probs = c(0.025, 0.975))))
colnames(bounds) <- c("lower", "upper")

e_df |> 
  as_tibble() |> 
  mutate(iter = 1:n()) |>
  pivot_longer(-iter, names_to = "series", values_to = "error") |>
  filter(series %in% high_levels) |>
  ggplot(aes(x = error)) +
    geom_histogram(bins = 30, fill = "lightblue", color = "black") +
    facet_wrap(~ series, ncol=2, scales = "free") +
    # geom_vline(data = as_tibble(bounds, rownames = "series") |> filter(series %in% high_levels),
    #            aes(xintercept = lower), color = "red", linetype = "dashed") +
    # geom_vline(data = as_tibble(bounds, rownames = "series") |> filter(series %in% high_levels),
    #            aes(xintercept = upper), color = "red", linetype = "dashed") +
    theme_minimal() +
    labs(title = "Distribution of 1-step ahead errors of MinT-Shr at high levels")

# summary stats of errors
psych::describe(e_df[, high_levels])[,c(1,3,4,11,12)] |> 
  as_tibble(rownames = "series")
```